### 2010-09-18 Documentation/tutorials/norm.tex
meeting-URL corrected. -ML

\GLOBES\ assumes that the cross
section $x$ is given in $10^{-38}\,\mathrm{cm}^2$, that all fluxes are
given at a distance of $1\,\mathrm{km}$ and the proper accounting for
the number of target nuclei $\tau$ (or protons or whatever applies to the
given cross section) per unit target mass $m_u$ (which usually is {\it
  kt}), is dealt with in the
definition of the flux inside \AEDL.  Assuming that in the flux file
the data is given as number of neutrinos per unit area $A$ and
energy bin of width $\Delta E$ at a distance $L$ from the source, one
obtains

\begin{eqnarray}
(\mathtt{@norm})^{-1}=5.20034\left(\frac{\Delta E}{\mathrm{GeV}}\right)\left(\frac{A}{\mathrm{cm}^2}\right)\left(\frac{\mathrm{km}}{L}\right)^2\left(\frac{\tau}{m_u}\right)\times10^{-38}\times\left(\frac{\mathcal{L}}{\mathcal{L}_u}\right)
\end{eqnarray}
where the $\mathcal{L}$ absorbs all factors in the flux file related to
the integrated luminosity and $\mathcal{L}_u$ is the unit chosen for
it.  The concept of integrated luminosity is
nicely described in the \GLOBES\ manual:

>>>>

\GLOBES\ assumes that the cross
section $x$ is given in $10^{-38}\,\mathrm{cm}^2$, that all fluxes are
given at a distance of $1\,\mathrm{km}$ and the proper accounting for
the number of target nuclei $\tau$ (or protons or whatever applies to the
given cross section\footnote{The cross section which come with
  \GLOBES\ always are per nucleon.}) per unit target mass $m_u$ (which usually is {\it
  kt}), is dealt with in the
definition of the flux inside \AEDL.  Assuming that in the flux file
the data is given as number of neutrinos per unit area $A$ and
energy bin of width $\Delta E$ at a distance $L$ from the source, one
obtains

\begin{eqnarray}
\mathtt{@norm}=\frac{1}{5.20034}\left(\frac{\mathrm{GeV}}{\Delta
      E}\right)
\left(\frac{\mathrm{cm}^2}{A}\right)\left(\frac{L}{\mathrm{km}}\right)^2\left(\frac{\tau}{m_u}\right)\times10^{-38}\times\left(\frac{\mathcal{L}_u}{\mathcal{L}}\right)
\end{eqnarray}
where the $\mathcal{L}$ absorbs all factors in the flux file related to
the integrated luminosity and $\mathcal{L}_u$ is the unit chosen for
it.  The concept of integrated luminosity is
nicely described in the \GLOBES\ manual:
